### 2013-10-01 Publications/2013-ISBI14/04-results.tex
Andres' comments
New figure 02, with binary connectivity matrices

\begin{figure*}[tpb]
   \centering
   \includegraphics[width=0.9\textwidth]{Fig02-Results}
   \caption{Visual comparison of correction methods results. 
   First row represents
   a coronal section of the \textit{b0} volume. In second row, the outcome
   of tractography, showing only tracks that connect two different
   network nodes. Third row shows the associated connectivity matrix. }
   \label{fig:results}
\end{figure*}

@@

The gold-standard contained a total of 1800 valid tracks
connecting regions, with an average length of $40.88\pm8.06$mm.
The corresponding connectivity matrix presented 25 connections 
between the total of 27 different seeding regions.

>>>>

\begin{figure*}[tpb]
   \centering
   \includegraphics[width=0.9\textwidth]{Fig02-Results}
   \caption{Visual comparison of correction methods results. 
   First row represents
   a coronal section of the \textit{b0} volume. In second row, the outcome
   of tractography after filtering tracks that did not connect two regions.
   Third row shows the associated connectivity matrices. First column shows
   the ground-truth. For the remaining steps, false positives have been marked
   in red color and false negatives in blue. Underlaying in gray color,
   the true positive (correctly detected) connections. }
   \label{fig:results}
\end{figure*}

@@

The gold-standard contained a total of 1800 valid tracks
connecting regions, with an average length of $40.88\pm8.06$mm.
The corresponding connectivity matrix presented 25 connections.
Results are presented in last row of \autoref{fig:results}.
